MachLensFinder - I: An automated Strong Lensing Identification Pipeline

### 2016-12-21 ms.tex
Added HOG visualizations for the sample mock images

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]\label{fig:hogvisual}
\begin{center}
\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or5ppc32cpb1.pdf}\hspace{-20pt}
\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or9ppc16cpb1.pdf}
\caption{Visualized HOG feature vectors of the sample lensed HST-like
  image from Figure~\ref{fig:mockimages}.  Left: The corresponding HOG
  visualization with N$_\text{orient}=5$, (32, 32) pixels per cell,
  and (1, 1) cells per block.  Right: The HOG visualization of the
  same mock image with N$_\text{orient}=9$, (16, 16) pixels per cell,
  and (1, 1) cells per block.  The brightest lines align with
  prominent edges.  Note, while fewer pixels per cell will better
  resolve the arc feature, the ``edge'' corresponding to the arc is
  less prominent.  }
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]\label{fig:hogvisual}
\begin{center}
\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or5ppc32cpb1.pdf}\hspace{-20pt}
\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or9ppc16cpb1.pdf}\\
\includegraphics[width=1\columnwidth]{figures/lsst_105_lensed_imgs_1or4ppc3cpb3.pdf}\hspace{-20pt}
\includegraphics[width=1\columnwidth]{figures/lsst_105_unlensed_imgs_1or4ppc3cpb3.pdf}\\
\includegraphics[width=1\columnwidth]{figures/lsst_stack_105_lensed_imgs_1or4ppc3cpb3.pdf}\hspace{-20pt}
\includegraphics[width=1\columnwidth]{figures/lsst_stack_105_unlensed_imgs_1or4ppc3cpb3.pdf}
\caption{Visualized HOG feature vectors of the sample lensed HST-like
  image from Figure~\ref{fig:mockimages}.  Left: The corresponding HOG
  visualization with N$_\text{orient}=5$, (32, 32) pixels per cell,
  and (1, 1) cells per block.  Right: The HOG visualization of the
  same mock image with N$_\text{orient}=9$, (16, 16) pixels per cell,
  and (1, 1) cells per block.  The brightest lines align with
  prominent edges.  Note, while fewer pixels per cell will better
  resolve the arc feature, the ``edge'' corresponding to the arc is
  less prominent.  }
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
